Exposure Consequences - Statistics and Figures

### 2018-02-02 ManuscriptMaterials.Rmd
put some participants back in, as I could not find why they were removed - one had a few missing files, so this resulted in no data at all when running some functions on partial datasets, this has been fixed

The absence of an interaction between training and target could be interpreted to mean that the generalization of reach aftereffects is the same after both kinds of training. Here are the confidence intervals for both:

@@

```{r loc_exp}
exposureLocalization()
```

@@

```{r loc_exp_movtype}
exposureLocalizationShift()
```

@@

```{r loc_ombnibus}
groupLocalization(model='full')
```

In the exposure group there is no effect of movement type, but we see one here. This could be because the effect of movement type is much larger in the classic group. This would predict an interaction between group and movement type, but this is a trend at best (p=.056). Hence we tested for an effect of movement type in the classic group:

```{r loc_cla}
classicLocalizationShift(remove15=TRUE)
classicLocalizationShift(remove15=FALSE)
```

@@

```{r}
multipleRegressionLocalization(group='exposure',NCpart='initial', LRpart='first')
```

@@

So this doesn't work either. Does this mean that in previous experiments we just didn't have sufficiently good data to find any link between classic reach aftereffects and (2-AFC) proprioceptive recalibration?

Do we still want to see online localization matches proprioception more, as claimed in Izawa et al., 2012? This would imply that it matches the exposure localization and/or reach aftereffects better...

>>>>

The absence of an interaction between training and target could be interpreted to mean that the generalization of reach aftereffects is the same after both kinds of training. Here are the confidence intervals for the peaks of both:

@@

```{r loc_exp}
exposureLocalization(remove15=TRUE)
```

@@

```{r loc_exp_movtype}
exposureLocalizationShift(remove15=TRUE)
```

@@

```{r loc_ombnibus}
groupLocalization(model='full',remove15=TRUE)
```

In the exposure group there is no effect of movement type, but we see one here. This could be because the effect of movement type is much larger in the classic group. This would predict an interaction between group and movement type, but this is not even a trend (p=.133). Hence we tested for an effect of movement type in the classic group:

```{r loc_cla}
classicLocalizationShift(remove15=TRUE)
```

@@

```{r}
# THIS FAILS NOW... maybe because some participants don't have data in the first half?
multipleRegressionLocalization(group='exposure',NCpart='initial', LRpart='first')
```

@@

So this doesn't work either.
